Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
shortned for submission

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We first evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \cite{immer2021improving}.
%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
% We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
% and run the experiment over $10$ random splits.
% That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
% for the neural network training as in the UCI experiments of
\cref{tbl:uci} (left) shows that \our with $M=256$ either matches or outperforms the predictive performance of the NN MAP, mean-field VI, Bayesian NN, and GLM
predictions %in terms of negative log-predictive density (NLPD).
(baselines from \cite{immer2021improving}).
That is, we match predictive performance despite being sparse.

In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
whilst using fewer inducing points.
\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
We provide further details of our experiments in \cref{app:uci}.
% as well as further results with varying number of inducing poitns ,64,128,256$
% We provide full details of our experiments as well as further experiments with varying number of inducing poitns and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
% benefits of \our in summarizing the full data distribution onto a small set of inducing
% points over just picking a random subset.

@@

\subsection{Supervised learning on image data sets}
\label{sec:image}

@@

Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
We report accuracy (ACC), NLPD, and expected calibration error (ECE).
For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
fix the number of inducing points $M=1024$.
For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
In this setting, we must rely on our GP's predictive mean.
% Other approaches, \cite{immer2021improving} never inten
% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.

>>>>

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We first evaluate \our on eight UCI benchmarks~\cite{UCI}, a variety of binary and multi-class classification tasks with different data set sizes.
We train a two-layer MLP for each of the classification tasks and follow the experiment set up in \cite{immer2021improving}.
%by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
% We follow \cite{immer2021improving} by using the same hyperparameters, performing a hyperparameter search over the prior precision $\delta$,
% and run the experiment over $10$ random splits.
% That is, after training we construct the \our dual and use the resulting model for uncertainty quantification.
% for the neural network training as in the UCI experiments of
\cref{tbl:uci} (left) shows that \our with $M=256$ either matches or outperforms the predictive performance of the NN MAP, mean-field VI, Bayesian NN, and GLM
predictions %in terms of negative log-predictive density (NLPD).
(baselines from \cite{immer2021improving}).
That is, we match predictive performance despite being sparse.
%
In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
whilst using fewer inducing points.
\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
We provide further details of our experiments in \cref{app:uci}.
% as well as further results with varying number of inducing poitns ,64,128,256$
% We provide full details of our experiments as well as further experiments with varying number of inducing poitns and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
% benefits of \our in summarizing the full data distribution onto a small set of inducing
% points over just picking a random subset.

@@

\subsection{Supervised learning on image data sets}
\label{sec:image}
Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures.
We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}).
After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}).
In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}.
We report accuracy (ACC), NLPD, and expected calibration error (ECE).
For \our and the GP predictive subset method by \cite{immer2021improving}, we provide results when predicting with GP mean and when using the neural network (NN) and
fix the number of inducing points $M=1024$.
For completeness, we also include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$.
The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points.
They further demonstrate that \our's predictive mean (GP) significantly outperforms the GP predictive subset.
This is an interesting result as we cannot rely on the NN's prediction if we wish to condition on new data, using the dual conditioning from \label{sec:sequential}.
In this setting, we must rely on our GP's predictive mean.
% Other approaches, \cite{immer2021improving} never inten
% The resutls demonstrate that \our's predictive GP mean significantly outperforms the
These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.

@@
